Reanalysis Step 4: Outcome Analysis with Three-Way Interaction

### 2025-08-17 reanalysis-4-outcome_analysis.qmd
wip

# Format for display
ame_display <- ame_results |>
  mutate(
    AME = round(AME, 4),
    SE = round(SE, 4),
    CI = paste0("(", round(CI_Lower, 4), ", ", round(CI_Upper, 4), ")"),
    P_Value = format.pval(2 * pnorm(-abs(AME/SE)), digits = 4, eps = 0.0001)
  ) |>
  select(DR_Severity, Treatment, N, AME, SE, CI, P_Value)

@@

if (!is.null(prob_col_name) && length(available_factor_cols) >= 3) {
  prob_table <- prob_df |>
    mutate(
      Probability = round(.data[[prob_col_name]], 3)
    ) |>
    select(all_of(available_factor_cols), Probability)

>>>>

# Format for display
ame_display <- ame_results |>
  mutate(
    AME = round(AME, 4),
    SE = round(SE, 4),
    CI = paste0("(", round(CI_Lower, 4), ", ", round(CI_Upper, 4), ")"),
    P_Value = format.pval(2 * pnorm(-abs(AME/SE)), digits = 4, eps = 0.0001)
  ) |>
  dplyr::select(DR_Severity, Treatment, N, AME, SE, CI, P_Value)

@@

if (!is.null(prob_col_name) && length(available_factor_cols) >= 3) {
  prob_table <- prob_df |>
    mutate(
      Probability = round(.data[[prob_col_name]], 3)
    ) |>
    dplyr::select(all_of(available_factor_cols), Probability)
